Semantic Textual Similarity using deep learning

### 2017-06-05 paper/main.tex
latex updated

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}

@@

\begin{table}[h!]
\caption{STS score description, adapted from~\citep{agirre2016semeval}}
\label{tab:sts-score}
\begin{center}
\begin{tabularx}{0.45\textwidth}{llr}
\toprule
Score & Explanation\\
\midrule
5 & \textit{Two sentences are completely equivalent}\\
& The bird is bathing in the sink\\
& Birdie is washing itself in the water basin.\\
\midrule
4 & \multicolumn{1}{m{6cm}}{\textit{The two sentences are mostly equivalent, but some unimportant details differ}} \\
  & \multicolumn{1}{m{6cm}}{In May 2010, the troops attempted to invade
Kabul.} \\
& \multicolumn{1}{m{6cm}}{The US army invaded Kabul on May 7th last
year, 2010.} \\
\midrule
3 & \multicolumn{1}{m{6cm}}{\textit{The two sentences are roughly equivalent, but some important information differs/missing.}} \\
  & \multicolumn{1}{m{6cm}}{John said he is considered a witness but not a
suspect.}\\
& ``He is not a suspect anymore.'' John said.\\
\midrule
2 & \multicolumn{1}{m{6cm}}{\textit{The two sentences are not equivalent, but share some details.}} \\
&They flew out of the nest in groups. \\
&They flew into the nest together. \\
\midrule
1 & \multicolumn{1}{m{6cm}}{\textit{The two sentences are not equivalent, but are on the same topic.}}\\
& The woman is playing the violin.\\
& The young lady enjoys listening to the guitar.\\
\midrule
0 & \textit{The two sentences are completely dissimilar.}\\
  & \multicolumn{1}{m{6cm}}{John went horse back riding at dawn with a whole group of friends.}\\
  & \multicolumn{1}{m{6cm}}{Sunrise at dawn is a magnificent view to take in if you wake up early enough for it.}\\
\bottomrule
\end{tabularx}
\end{center}
\end{table*}

@@

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \includegraphics[width=\columnwidth]{sen_len_no_stop.png}
		\caption{Sentence lengths without stopwords}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \includegraphics[width=\columnwidth]{sen_len_with_stop.png}
		\caption{Sentence lengths with stopwords}
    \end{subfigure}
    ~
    \caption{Sentence length stats}
\end{figure*}

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[t]{0.47\textwidth}
		\includegraphics[width=\columnwidth]{tokens_no_stop.png}
		\caption{Number of tokens without stopwords}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.49\textwidth}
		\includegraphics[width=\columnwidth]{tokens_with_stop.png}
		\caption{Number of tokens with stopwords}
    \end{subfigure}
    ~
    \caption{Number of tokens stats}
\end{figure*}

@@

\begin{figure*}[h!]
\begin{center}
	\centering
	\includegraphics[scale=0.36]{R2.png}
	\caption{R2 score}
\end{center}
\end{figure*}

\begin{figure*}[h!]
\begin{center}
	\centering
	\includegraphics[scale=0.36]{Pearson.png}
	\caption{Pearson correlation score}
\end{center}
\end{figure*}

\begin{table}
\caption{Averaged scores}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{ccc}
\toprule
& R2 & Pearson\\
\midrule
score & 0.5898 & 0.7795 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

Deep neural networks have been shown to perform well on language modelling tasks
(insert citation). Use of highly non-linear functions in the models allows for learning of information on a high level of abstraction. Semantic textual similarity bla bla idem spavat sutra ovo dovrsim.

\subsection{All results}

Table \ref{tab:all_results} shows the performance of all tested models.
Bla bla we draw some conclusion from this?
\begin{table}
	\caption{Model comparison}
\label{tab:all_results}
\begin{center}
\begin{tabular}{ccc}
\toprule
Model & Pearson coefficient \\
\midrule
Jaccard similarity & 0.73 \\
Cosine baseline & 0.73 \\
LSTM & 0.59 \\
SVM & 0.78 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{table*}
\caption{STS score description, adapted from~\citep{agirre2016semeval}}
\label{tab:sts-score}
\begin{center}
\begin{tabular}{llr}
\toprule
Score & Explanation\\
\midrule
5 & \textit{Two sentences are completely equivalent}\\
& The bird is bathing in the sink\\
& Birdie is washing itself in the water basin.\\
\midrule
4 & \textit{The two sentences are mostly equivalent, but some unimportant details differ}\\
& In May 2010, the troops attempted to invade
Kabul. \\
& The US army invaded Kabul on May 7th last
year, 2010.\\
\midrule
3 & \textit{The two sentences are roughly equivalent, but some important information differs/missing.}\\
& John said he is considered a witness but not a
suspect.\\
& ``He is not a suspect anymore.'' John said.\\
\midrule
2 & \textit{The two sentences are not equivalent, but share some details.} \\
&They flew out of the nest in groups. \\
&They flew into the nest together. \\
\midrule
1 & \textit{The two sentences are not equivalent, but are on the same topic.}\\
& The woman is playing the violin.\\
& The young lady enjoys listening to the guitar.\\
\midrule
0 & \textit{The two sentences are completely dissimilar.}\\
& John went horse back riding at dawn with a whole group of friends.\\
& Sunrise at dawn is a magnificent view to take in if you wake up early enough for it.\\
\bottomrule
\end{tabular}
\end{center}
\end{table*}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \includegraphics[width=\columnwidth]{sen_len_no_stop.png}
		\caption{Sentence lengths without stopwords}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{0.5\textwidth}
        \includegraphics[width=\columnwidth]{sen_len_with_stop.png}
		\caption{Sentence lengths with stopwords}
    \end{subfigure}
    ~
    \caption{Sentence length stats}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.47\textwidth}
		\includegraphics[width=\columnwidth]{tokens_no_stop.png}
		\caption{Number of tokens without stopwords}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.49\textwidth}
		\includegraphics[width=\columnwidth]{tokens_with_stop.png}
		\caption{Number of tokens with stopwords}
    \end{subfigure}
    ~
    \caption{Number of tokens stats}
\end{figure*}

@@

\begin{figure*}
\begin{center}
	\centering
	\includegraphics[scale=0.36]{R2.png}
	\caption{R2 score}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
	\centering
	\includegraphics[scale=0.36]{Pearson.png}
	\caption{Pearson correlation score}
\end{center}
\end{figure*}

\begin{table}
\caption{Averaged scores}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{ccc}
\toprule
& R2 & Pearson\\
\midrule
score & 0.5898 & 0.7795 \\
std & 0.011393 & 0.006625 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@
